### 2023-02-02 README.Rmd
Updates version 0.1.1

# View the estimates, confidence intervals, and p-values;
# they are the same as when using sim_ame() above
summary(sim_est, null = c(NA, NA, 1))

@@

```{r}
#Transform estimates into new quantities of interest
sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
summary(sim_est, null = c(NA, NA, 1, 0))
```

>>>>

# View the estimates, confidence intervals, and p-values;
# they are the same as when using sim_ame() above
summary(sim_est, null = c(`RR` = 1))

@@

```{r}
#Transform estimates into new quantities of interest
sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
summary(sim_est, null = c(`RR` = 1, `RD` = 0))
```
